---
title: "Assignment 5"
author: "Hongyi He,Glib, Hong Chen"
date: "2018Äê3ÔÂ18ÈÕ"
output: slidy_presentation
---

```{r, echo = T, include=F}
library(tidyverse)
library(readxl)
library(stringr)
library(ggplot2)
```

# 1.Daily timeseries plot

  The rows in red is LD50 meaning the amount of a toxic agent that is sufficient to kill 50 percent of a population of animals usually within a certain time, the unit of which is mg/kg.
  The blue rows is Real indicating that the chemical facts in Brocoli, the unit of which is lbs.

```{r, echo = F}
chemical_tox <- read.csv("chemical_tox.csv")

veg_data3<-read.csv("veg_data3.csv")

veg_data3<-as.tibble(veg_data3)

veg_data3$Value <- as.numeric(veg_data3$Value)

#get the data with toxicity info in it

chemical_tox <- as.tibble(chemical_tox)

chemical_tox$X <- as.integer(chemical_tox$X)

chemical_tox$Name <- as.character(chemical_tox$Name)

chemical_tox$ID <- as.character(chemical_tox$ID)

chemical_tox <- chemical_tox %>% select(-ID)

broc <- veg_data3 %>% filter(label == "RESTRICTED USE CHEMICAL", Commodity == "BROCCOLI", Unit.of.Measurement==" MEASURED IN LB")

broc$Value <- as.numeric(broc$Value)

broc <- left_join(broc,chemical_tox,by="Name")

broc <- rename(broc,Real=Value,LD50=X)

broc <- broc %>% gather(Real , LD50 , key="Toxicity", value="value")

ggplot(broc, aes(x= Name, y=value )) + 
  geom_bar(stat="identity",position = "dodge",aes(fill=Toxicity)) + 
  labs(y = "Values(LB) ",x = "Chemical Name") +
  coord_flip()+
  labs(title="LD50(mg/kg) and Real content(lb) of Brocoli")
```

# 2.Chemicals in Cauliflower

 The rows in red is LD50 meaning the amount of a toxicity is sufficient to kill 50 percent of a population of animals usually within a certain time, the unit of which is mg/kg.
 The blue rows is Real indicating that the chemical facts in Cauliflowcer, the unit of which is lbs.

```{r,echo = F}
Caul <- veg_data3 %>% filter(label == "RESTRICTED USE CHEMICAL", Commodity == "CAULIFLOWER", Unit.of.Measurement==" MEASURED IN LB")

Caul$Value <- as.numeric(Caul$Value)

Caul <- left_join(Caul,chemical_tox,by="Name")

Caul <- rename(Caul,Real=Value,LD50=X)

Caul <- Caul %>% gather(Real , LD50 , key="Toxicity", value="value")

#plot the Cauliflower 
ggplot(Caul, aes(x= Name, y=value )) + 
  geom_bar(stat="identity",position = "dodge",aes(fill=Toxicity)) + 
  labs(y = "Values(LB) ",x = "Chemical Name") +
  coord_flip()+
  labs(title="LD50(mg/kg) and Real content(lb) of Cauliflower")
```

